Spatio-Temporal Modeling and Simulation

### 2024-06-10 report/Report.tex

$$\partial_Z \left[ \sum_{jk}\left( \delta \hat{G}_{jk} - u_{jki}\right)^2 \right] = \sum_{\phi_{jki} \in Z} 2\left( \delta \hat{G}_{jk} - u_{jki}\right) = \sum_{\phi_{jki} \in Z} \delta \hat{G}_{jk} - \sum_{\phi_{jki} \in Z} u_{jki}$$

@@

which means that in order for our partial derivative above to be zero (and therefore our error term be at a minimum) that $\delta \hat{G}_{jk}=0$. And this means our iteration will have stopped!

>>>>

$$\partial_Z \left[ \sum_{jk}\left( \delta \hat{G} - u_{jki}\right)^2 \right] = \sum_{\phi_{jki} \in Z} 2\left( \delta \hat{G} - u_{jki}\right) = 2\sum_{\phi_{jki} \in Z} \delta \hat{G} - 2\sum_{\phi_{jki} \in Z} u_{jki}$$

@@

which means that in order for our partial derivative above to be zero (and therefore our error term be at a minimum) that $\delta \hat{G}=0$. And this means our iteration will have stopped!
